---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)


# gnet

The goal of gnet is to ...

## Installation

You can install the released version of gnet from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("gnet")
```

## Support

This material is based upon work support by, or in part by, the U.S.
Army Research Laboratory and the U.S. Army Research Office under
grant number W911NF-15-1-0577

Computation for the work described in this paper was supported by
the University of Southern California's Center for High-Performance
Computing (hpcc.usc.edu).

## Example

This is a basic example which shows you how to solve a common problem:

```{r example1, cache=FALSE}
library(ergmito)
library(gnet)


# A random sample of networks
set.seed(12)
nets <- rbernoulli(c(3,3,4,4,4))

# Are the edgecounts random??
fun <- function(g, y) mean(count_stats(g, "edges") - y, na.rm = TRUE)

mytest01 <- struct_test(nets ~ edges + balance, y = runif(5), R=1000, stat=fun)
```

```{r printing}
mytest01
```


```{r hist}
# Looking at the distribution
hist(mytest01$t, breaks=10, col="gray", border="transparent")
abline(v = mytest01$t0, col="steelblue", lwd=2, lty="dashed")
```

Using the fivenets dataset included in `ergmito`. In this example, we show how the model can be use to discover an association between 

```{r fivenets}

# Loading the fivents dataset. We actually know that data generating process,
# so we use these paramaters for the model
data(fivenets, package="ergmito")

# We will generate a group level variable that is related to the proportion of
# females in the group
set.seed(52)
y <- count_stats(fivenets ~ nodematch("female"))
y <- y + rnorm(nnets(fivenets), sd = 2)

# Performing the struct test
f02 <- function(g, y) cor(count_stats(g ~ nodematch("female")), y, use = "complete.obs")[1] 
mytest02 <- struct_test(
  fivenets ~ edges + nodematch("female"), y = y, R=2000,
  stat = f02
  )
mytest02

hist(mytest02$t, breaks=10, col="gray", border="transparent")
abline(v = mytest02$t0, col="steelblue", lwd=2, lty="dashed")
```

What would have we got if we use correlation or a linear regression only?

```{r}
# Pearson correlation
x <- count_stats(fivenets ~ nodematch("female"))

cor.test(x, y)
summary(lm(y ~ x))
```

In this case, the test has higher power than the other 2.

